WHOOMP! (There It Is) \\ Rapid Bayesian position reconstruction for gravitational\nobreakdashes-wave transients

### 2014-05-29 ms.tex
Fold factor of 1/2 into weight function
Some arguments why w(t,r) approaches a delta function

Fisher matrix elements of \Eref{eq:autocor-likelihood}, with detector subscript suppressed:
%
\begin{eqnarray}
	\nonumber
	\mathcal{I}_{\rho\rho} &=& 1 \\
	\nonumber
	\mathcal{I}_{\rho\gamma} &=& 0 \\
	\nonumber
	\mathcal{I}_{\rho\tau} &=& 0 \\
	\mathcal{I}_{\gamma\gamma} &=& \frac{\rho^2}{2}
		\int_{-\infty}^\infty \left|a(t)\right|^2 w(t; \rho) dt \\
	\mathcal{I}_{\tau\tau} &=& -\frac{\rho^2}{2}
		\int_{-\infty}^\infty \Re\left[a^*(t) a''(t)\right] w(t; \rho) dt \\
	\mathcal{I}_{\gamma\tau} &=& -\frac{\rho^2}{2}
		\int_{-\infty}^\infty \Im\left[a^*(t) a'(t)\right] w(t; \rho) dt \\
	\nonumber\textrm{where} && \\
	\nonumber
	a'(t) &=& \frac{\partial a}{\partial t} \\
	\nonumber
	a''(t) &=& \frac{\partial^2 a}{\partial t^2} \\
	\nonumber
	w(t; \rho) &=& \frac{
		\displaystyle
		\exp\left[\frac{\rho^2}{4}\left|a(t)\right|^2\right]
		\left(
		I_0\left[\frac{\rho^2}{4}\left|a(t)\right|^2\right] +
		I_1\left[\frac{\rho^2}{4}\left|a(t)\right|^2\right]
		\right)
	}{
		\displaystyle
		\int_{-\infty}^\infty
		\exp\left[\frac{\rho^2}{4}\left|a(t')\right|^2\right]
		I_0\left[\frac{\rho^2}{4}\left|a(t')\right|^2\right]
		dt'
	}.
\end{eqnarray}

If we can show that the common factor approaches a delta function, $w(t; \rho) \rightarrow \delta(t)$ as $\rho \rightarrow \infty$, then the Fisher matrix approaches \Eref{eq:fisher-matrix} as $\rho \rightarrow \infty$.

>>>>

Fisher matrix elements of \Eref{eq:autocor-likelihood}, with detector subscript suppressed:
%
\begin{eqnarray}
	\nonumber
	\mathcal{I}_{\rho\rho} &=& 1 \\
	\nonumber
	\mathcal{I}_{\rho\gamma} &=& 0 \\
	\nonumber
	\mathcal{I}_{\rho\tau} &=& 0 \\
	\mathcal{I}_{\gamma\gamma} &=& \rho^2
		\int_{-\infty}^\infty \left|a(t)\right|^2 w(t; \rho) dt \\
	\mathcal{I}_{\tau\tau} &=& -\rho^2
		\int_{-\infty}^\infty \Re\left[a^*(t) a''(t)\right] w(t; \rho) dt \\
	\mathcal{I}_{\gamma\tau} &=& -\rho^2
		\int_{-\infty}^\infty \Im\left[a^*(t) a'(t)\right] w(t; \rho) dt \\
	\nonumber\textrm{where} && \\
	\nonumber
	a'(t) &=& \frac{\partial a}{\partial t} \\
	\nonumber
	a''(t) &=& \frac{\partial^2 a}{\partial t^2} \\
	\nonumber
	w(t; \rho) &=& \frac{
		\displaystyle
		\exp\left[\frac{\rho^2}{4}\left|a(t)\right|^2\right]
		\left(
		I_0\left[\frac{\rho^2}{4}\left|a(t)\right|^2\right] +
		I_1\left[\frac{\rho^2}{4}\left|a(t)\right|^2\right]
		\right)
	}{
		\displaystyle
		2 \int_{-\infty}^\infty
		\exp\left[\frac{\rho^2}{4}\left|a(t')\right|^2\right]
		I_0\left[\frac{\rho^2}{4}\left|a(t')\right|^2\right]
		dt'
	}.
\end{eqnarray}
%
Matrix elements that are not listed have values that are implied by the symmetry of the Fisher matrix. Note that the minus signs are correct but a little confusing: despite them, ${I}_{\gamma\gamma}, {I}_{\tau\tau} \geq 0$ and ${I}_{\gamma\tau} \leq 0$.

If we can show that the common factor approaches a delta function, $w(t; \rho) \rightarrow \delta(t)$ as $\rho \rightarrow \infty$, then the Fisher matrix approaches \Eref{eq:fisher-matrix} as $\rho \rightarrow \infty$. Certainly it behaves very much like a delta function. The Bessel functions asymptotically approach:
%
\begin{equation*}
	I_0(x), I_1(x) \rightarrow \frac{e^x}{\sqrt{2 \pi x}}
	\textrm{ as } x \rightarrow \infty.
\end{equation*}
%
For large $\rho$, it seems like we could write:
%
\begin{equation*}
	w(t; \rho) \rightarrow \frac{
		\displaystyle
		\exp\left[\frac{\rho^2}{2}|a(t)|^2\right]
	}{
		\displaystyle
		\int_{-\infty}^\infty \exp\left[\frac{\rho^2}{2}|a(t')|^2\right] dt'
	}
	\textrm{ as } \rho \rightarrow \infty.
\end{equation*}
